### 2013-08-14 main.tex
ideen fuer zusaetzliches material, intro datei / gliederung
update jmlr paper in thesis
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.
add some aknowledgements

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{listings}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
%\usepackage{layout}

@@

\newcommand{\x}{\checkmark}
\renewcommand{\o}{$\times$}
\newcommand{\pystruct}{{\sc PyStruct} }

@@

\begin{document}
%\layout

@@

%\listoffigures
%\listoftables
\chapter*{Acknowledgements}

@@

\chapter{introduction}

@@

\chapter{Concepts and Implementation of Conditional Random Field-based Semantic Segmentation}

@@

\bibliographystyle{plainnat}
\bibliography{main}
\end{document}

>>>>

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
\usepackage{xspace}

@@

\newcommand{\x}{\checkmark}
\renewcommand{\o}{$\times$}

\definecolor{rulecolor}{rgb}{0.80,0.80,0.80}
\newminted{python}{frame=single,rulecolor=\color{rulecolor}, linenos, xleftmargin=7mm}

\newcommand{\pystruct}{\textsc{PyStruct}\xspace}
\newcommand{\svmstruct}{SVM$^\text{struct}$\xspace}

@@

\begin{document}

@@

%\listoffigures
%\listoftables
\chapter*{Abstract}

\chapter*{Acknowledgements}
First, I would like to thank my advisor Sven Behnke, who allowed me
to pursue my PhD in his department and who provided funding for my studies.
Juergen fuer review?

During my work on this dissertation, my ideas where shape by many of my fellow
students and researchers. First and foremost I am indept to Hannes Schulz,
whose feedback proved invaluable during my studies.
I would like to thank Christoph Lampert, for hosting me as visiting Researcher
at the IST Austria. His guidance and advice.

Carsten Rother, Sebastian Nowozin

Cristian Sminchisescu?
Phillip, Victoriia, Aurelien, Theo

I have been lucky to be a part of the scikit-learn community, whos developers
have been a constant source of encouragement and feedback to me. My understanding
of machine learning as well as software engineering has been greatly affected
by the constant exchange with Olivier Grisel, Lars Buitinck, Gael Varoquax,
Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and others.

Last but not least I am greatful to Anna M\uller for her support, encouragement and company
Thank you for giving me the strength needed for this endeavour.

@@

\chapter{Overview}
\include{intro.tex}

@@

\chapter{Concepts and Implementation of Conditional Random Field-based Semantic Segmentation}\label{structured_pystruct}

@@

\bibliographystyle{plainnat}
\bibliography{main}
\include{mil/appendix}
\end{document}
